---
title: "Article Sample"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(jsonlite)
library(here)

dir <- here()

seedling <- 7215887
set.seed(seedling)

#number of articles per strata
n_articles <- 1500

```

Read in the json files and then sample a set of articles.

```{r jsonload, eval=FALSE, include=FALSE}

#load a json file.

sample_frame <- stream_in(file(paste0(dir, "/01_raw_data/metadata/included/metadata_0.jsonl")))

save(sample_frame, file=paste0(dir, "/01_raw_data/metadata/included/metadata_0.Rdata"))

```


```{r}

load(paste0(dir, "/01_raw_data/metadata/included/metadata_0.Rdata"))


```

```{r}
excluded_fields <- c('Biology','Chemistry', 'Engineering', 'Physics','Materials Science', 'Geology', 'Art')

sample_restricted1 <- sample_frame %>%
  filter(!is.na(abstract)) 

abstract_restrict <- (nrow(sample_frame) - nrow(sample_restricted1))/nrow(sample_frame)

sample_restricted2 <- sample_restricted1 %>%
  filter(year>2000) 

year_restrict <- (nrow(sample_restricted1) - nrow(sample_restricted2))/nrow(sample_frame)

sample_restricted <- sample_restricted2 %>% #keep just recent articles
  mutate(
    group_name=case_when( #specify  for each field type. 
      grepl('Economics', mag_field_of_study)  ~ 'Economics',
      grepl('Political Science', mag_field_of_study)  ~ 'Political Science',
      grepl('Business', mag_field_of_study)  ~ 'Business',
      grepl('Sociology'	, mag_field_of_study)  ~ 'Sociology',
      grepl('Medicine', mag_field_of_study) ~ 'Medicine',
      grepl('Computer Science', mag_field_of_study)  ~ 'Computer Science',
      grepl('Math'	, mag_field_of_study)  ~ 'Math',
      grepl('Psychology', mag_field_of_study)	 ~ 'Psychology',
      grepl('Geography'	, mag_field_of_study)  ~ 'Geography',
      grepl('History'	, mag_field_of_study)  ~ 'History',
      grepl('Philosophy'	, mag_field_of_study)  ~ 'Philosophy',
      grepl('Biology', mag_field_of_study) ~ 'Biology', #excluded
      grepl('Chemistry', mag_field_of_study)  ~ 'Chemistry', #excluded
      grepl('Engineering', mag_field_of_study)  ~ 'Engineering', #excluded	
      grepl('Physics', mag_field_of_study)	 ~ 'Physics', #excluded
      grepl('Material Science', mag_field_of_study)  ~ 'Material Science', #excluded
      grepl('Geology'	, mag_field_of_study)  ~ 'Geology', #excluded
      grepl('Environmental Science'	, mag_field_of_study) ~ 'Environmental Science', #excluded
      grepl('Art'	, mag_field_of_study)  ~ 'Art', #excluded
      TRUE ~ 'Other'),
    
    sample_share=case_when( #specify the fraction of the sample for each field type.  Oversample development fields
      group_name=='Medicine' ~ .15,
      group_name=='Biology' ~ 0, #excluded
      group_name=='Chemistry'  ~ 0, #excluded
      group_name=='Engineering'  ~ 0, #excluded	
      group_name=='Computer Science'  ~ 0, #excluded
      group_name=='Physics'	 ~ 0, #excluded
      group_name=='Material Science'  ~ 0, #excluded
      group_name=='Math'	  ~ 0, #excluded
      group_name=='Psychology'	 ~ .15,
      group_name=='Economics'  ~ .25,
      group_name=='Political Science'  ~ .25,
      group_name=='Business'  ~ .10,
      group_name=='Geology'	  ~ 0, #excluded
      group_name=='Sociology'	  ~ .10,
      group_name=='Geography'	  ~ 0, #excluded
      group_name=='Environmental Science'	 ~ 0, #excluded
      group_name=='Art'	  ~ 0, #excluded
      group_name=='History'	  ~ 0, #excluded
      group_name=='Philosophy'	  ~ .0, #excluded
      TRUE ~ 0)
    )  %>%
  filter(sample_share>0) %>% #remove excluded fields
  group_by(group_name) %>% 
  mutate(field_count=n()) %>%
  ungroup() %>%
  mutate(field_share=field_count/n(),
         total_count=n())


field_restrict <-  (nrow(sample_restricted2) - nrow(sample_restricted))/nrow(sample_frame)


write_excel_csv(sample_restricted, file=paste0(dir, "/03_output/sample/sample_frame_",Sys.Date(),".csv"))


```


```{r}
#read in the list of files
file_list<- list.files(paste0(dir, "/03_output/sample/"))


#turn into dataframe and read
previous_samples_df <- data.frame(batch=file_list)

#read the files
previous_samples_df <- previous_samples_df %>%
  mutate(Data=map(
    batch, ~read_csv(file=paste0(dir, "/03_output/sample/",.))
  )) %>%
  unnest(Data) %>%
  transmute(
    paper_id=as.character(paper_id),
    title=title,
    abstract=abstract,
    sampled='Previously Sampled'
  )

#drop articles already sampled
sample_restricted <- sample_restricted %>%
  left_join(previous_samples_df) %>%
  filter(is.na(sampled))

```

Draw sample.

The frame is divided into groups based on the major field of study of the article.  Each field has a pre-specified share of articles that are define above.  Within each field (strata) the probability of selection is equal for all articles in the strata.  Simple random sampling within strata.  

For each strata (Field of study), $j$ the probability an article is selected is:

$$ p_j=\frac{n}{N} $$

where n is the number of articles to be chosen in the field, and N is the total number of articles within that field.

The sample weights then


```{r}

sample_selected <- sample_restricted %>%
  group_by(group_name) %>%
  sample_n(size=n_articles*sample_share) %>%
  select(paper_id, title, abstract, year, journal, doi, mag_field_of_study, has_pdf_parse, has_pdf_parsed_abstract, has_pdf_parsed_body_text , s2_url, group_name, sample_share, field_count, field_share) %>%
  mutate(seed=seedling,
         n_articles=n_articles)

```

Check if any articles have been sampled before
```{r}

overlap_df <- previous_samples_df %>%
  inner_join(sample_selected)

#should be zero rows
nrow(overlap_df)
```


```{r}
sample_selected %>% group_by(group_name,sample_share, field_count, field_share) %>% summarise(n=n())
```

Save to csv
```{r}
write_excel_csv(sample_selected, file=paste0(dir, "/03_output/sample/selection_",Sys.Date(),".csv"))


```

